New lower bounds for Schur and weak Schur numbers

### 2021-04-14 article/appendix.tex
reorganisation sat / search space

>>>>

\section{Reformulation as a SAT problem}
\label{SAT}

In this section, we reframe the question of the existence of (weakly) sum-free partitions as a boolean
satisfiability (SAT) problem. We encode the existence of (weakly) sum-free partitions as propositional formulae like in
\cite{Heule2017} and then use SAT solvers to determine whether these formulae are satisfiable.

\begin{definition}
A \textit{literal} is either a variable \(v\) (a positive literal) or the negation \(\bar{v}\) of a variable \(v\) (a
negative literal) where \(v\)
takes a truth value: \(true\) or \(false\). A \textit{clause} is a disjunction of literals and a \textit{formula} is a
conjunction of clauses: it
is a propositional formula in \textit{conjonctive normal form} (CNF).
\end{definition}

\begin{definition}
An \textit{assignment} is a function from a set of variables to the truth values \(true\) (1) and \(false\) (0). A
literal \(l\) is
\textit{satisfied} (\textit{falsified}) by an assignment \(\alpha\) if l is positive and \(\alpha(var (l)) = 1\)
(resp. \(\alpha(var (l)) = 0\)) or if it is negative and \(\alpha(var (l)) = 0\) (resp. \(\alpha(var (l)) = 1\)). A
clause is \textit{satisfied}
by an assignment \(\alpha\) if it contains a literal that is satisfied by \(\alpha\). Finally, a formula is
\textit{satisfied} by an assignment
\(\alpha\) if all its clauses are satisfied by \(\alpha\). A formula is \textit{satisfiable} if there exists an
assignment that satisfies it;
otherwise it is \textit{unsatisfiable}.
\end{definition}

We then encode the existence of a partition of \([\![1,p]\!]\) in \(k\) weakly sum-free subsets as follows: for every
integer
\(i \in [\![1,p]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!],
x^{(i)}_c = 1 \iff i \in A_c\).
The corresponding clauses are:

\begin{itemize}
\item \textbf{weakly sum-free:} \(\forall c \in [\![1,k]\!], \forall (i, j) \in [\![1,p]\!]^2, (i \neq j ~ \text{and} ~ i + j
\leq n) \implies \lnot x^{(i)}_c
\lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
\item \textbf{union:} \(\forall i \in [\![1,p]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
\item \textbf{disjoint:} \(\forall i \in [\![1,p]\!],\forall (c_1, c_2) \in [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg
x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
\end{itemize}

In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the
subsets, that is by
enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
\textbf{symmetry breaking:} \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1, \WS (c - 1)+1]\!],
x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)

\begin{remark}
For a given problem, it can be interesting to try out different SAT solvers because the relative performance can vary
significantly according to the problem.
For instance, we used two different SAT solvers in the next two next subsections.
\end{remark}

\begin{remark}
Using a parallel SAT solver usually reduces the computation time, especially when trying to show that a formula is
unsatisfiable. However, most of the
parallel SAT solver do not have a deterministic behaviour and it can results in a strong variation of running times.
\end{remark}

### 2021-04-14 article/search_space.tex
reorganisation sat / search space

\section{About the construction of lower bounds for weak Schur numbers using a computer}

In this section, we first reframe the question of the existence of (weakly) sum-free partitions as a boolean
satisfiability (SAT) problem. We then provide evidence which indicates that the main assumption made by papers which
found the previous best known lower bounds for weak Schur numbers may not be correct. Finally, we obtain stronger
results than those previously known for \(\WS (5)\) while gaining several orders of magnitude in computation time by
giving additional information to the SAT solver without losing in generality. In this section, we assume that the
subsets are ordered.

\subsection{Reformulation as a SAT problem}
\label{SAT}

We encode the existence of (weakly) sum-free partitions as propositional formulae like in
\cite{Heule2017} and then use
SAT solvers to determine whether these formulae are satisfiable.

\begin{definition}
A \textit{literal} is either a variable \(v\) (a positive literal) or the negation \(\bar{v}\) of a variable \(v\) (a
negative literal) where \(v\)
takes a truth value: \(true\) or \(false\). A \textit{clause} is a disjunction of literals and a \textit{formula} is a
conjunction of clauses: it
is a propositional formula in \textit{conjonctive normal form} (CNF).
\end{definition}

\begin{definition}
An \textit{assignment} is a function from a set of variables to the truth values \(true\) (1) and \(false\) (0). A
literal \(l\) is
\textit{satisfied} (\textit{falsified}) by an assignment \(\alpha\) if l is positive and \(\alpha(var (l)) = 1\)
(resp. \(\alpha(var (l)) = 0\)) or if it is negative and \(\alpha(var (l)) = 0\) (resp. \(\alpha(var (l)) = 1\)). A
clause is \textit{satisfied}
by an assignment \(\alpha\) if it contains a literal that is satisfied by \(\alpha\). Finally, a formula is
\textit{satisfied} by an assignment
\(\alpha\) if all its clauses are satisfied by \(\alpha\). A formula is \textit{satisfiable} if there exists an
assignment that satisfies it;
otherwise it is \textit{unsatisfiable}.
\end{definition}

We then encode the existence of a partition of \([\![1,p]\!]\) in \(k\) weakly sum-free subsets as follows: for every
integer
\(i \in [\![1,p]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!],
x^{(i)}_c = 1 \iff i \in A_c\).
The corresponding clauses are:

\begin{itemize}
\item \textbf{sumfree:} \(\forall c \in [\![1,k]\!], \forall (i, j) \in [\![1,p]\!]^2, (i \neq j ~ \text{and} ~ i + j
\leq n) \implies \lnot x^{(i)}_c
\lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
\item \textbf{union:} \(\forall i \in [\![1,p]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
\item \textbf{disjoint:} \(\forall i \in [\![1,p]\!],\forall (c_1, c_2) \in [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg
x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
\end{itemize}

In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the
subsets, that is by
enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
\textbf{symmetry breaking:} \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1, \WS (c - 1)+1]\!],
x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)

\begin{remark}
For a given problem, it can be interesting to try out different SAT solvers because the relative performance can vary
significantly according to the problem.
For instance, we used two different SAT solvers in the next two next subsections.
\end{remark}

\begin{remark}
Using a parallel SAT solver usually reduces the computation time, especially when trying to show that a formula is
unsatisfiable. However, most of the
parallel SAT solver do not have a deterministic behaviour and it can results in a strong variation of running times.
\end{remark}

\subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
Rowley's new lower bound for \(\WS (6)\) (642) \cite{RowleyWS} was a quite significant improvement upon
the former
best known lower bound (582) \cite{EliahouBook}. This previous lower bound was found using a computer
(often with Monte-Carlo methods) and by making the
assumption that a good partition for \(\WS (n+1)\) starts with a good partition for \(\WS (n)\) which is true for small
values of \(n\).
Therefore, one may wonder whether the limiting factor are the assumptions or the methods used to search for partitions.
It appears that the search space
induced by these assumptions does not contain the optimal partitions.

@@

For \(m_4 = 24\), the value \(m_5 \leqslant 53\) was obtained after 7 hours of runtime, and for  \(m_4 = 22\), the
value \(m_5 \leqslant 59\) was obtained after 11 hours of runtime. All the other values took between 1 minutes and 2 hours.
To obtain these results, we once again provided additionnal information to the SAT solver. We added two different types information.
The first one is the same as previously: we compute the subsets in which the first numbers can appear. The second type of
information is the maximum length of a sequence using only a certain subset of the colors. For instance,
if \(m_4 \geqslant 22\), then there cannot be more than 17 consecutive numbers with color 1, 2 or 3. \\

>>>>

\section{Analysis of the former search space}

In this section, we first provide evidence which indicates that the main assumption made by papers which
found the previous best known lower bounds for weak Schur numbers using a computer may not be correct. 
This is done primarily by studying \(\WS(6)\). Then, in an effort to eliminate irrelevant search spaces, we 
obtain stronger results than those previously known for \(\WS (5)\) while gaining several orders of magnitude 
in computation time by giving additional information to the SAT solver without losing in generality. In this 
section, we assume that the subsets are ordered.

\subsection{Former assumption appears to be wrong}
Rowley's new lower bound for \(\WS (6)\) (642) \cite{RowleyWS} was a significant improvement upon
the former best known lower bound (582) \cite{EliahouBook}. This previous lower bound has been found 
several times using a computer (often with Monte-Carlo methods) and by recursively making the assumption 
that a good partition for \(\WS (n+1)\) starts with a good partition for \(\WS (n)\) which is true for small
values of \(n\). Therefore, one may wonder whether the limiting factor are the assumptions or the 
methods used to search for partitions. It appears that the search space induced by these assumptions does 
not contain the optimal partitions.

@@

For \(m_4 = 24\), the value \(m_5 \leqslant 53\) was obtained after 7 hours of runtime, and for  \(m_4 = 22\), the
value \(m_5 \leqslant 59\) was obtained after 11 hours of runtime. All the other values took between 1 minutes and 2 hours.
To obtain these results, we once again provided additionnal information to the SAT solver. We added two different types information.
The first one is the same as previously: we compute the subsets in which the first numbers can appear. The second type of
information is the maximum length of a sequence using only a certain subset of the colors. For instance,
if \(m_4 \geqslant 22\), then there cannot be more than 17 consecutive numbers with color 1, 2 or 3.

\subsection{Conclusion on the search space}
As explained in the first subsection, the recursive assumption that a good partition for\(\WS (n+1)\) starts with a good partition for 
\(\WS (n)\) appears to be wrong. Given that no extensive search for \(\WS(5)\) has been conducted without making this assumption and 
that the size of the considered partitions is reasonable (the current lower bound is 196 and \(S(5) = 160\) was verified), it seems worth 
investigating this special case further. In a spirit of orientating this search, we then give necessary conditions on an hypothetical partition 
of \([\![1,197]\!]\) in 5 weakly sum-free subsets. Finding partitions that exceeds the lower bounds found with a computer (even if they 
do not exceed those obtained with templates) which are not as regular as those obtained with templates would be extremely interesing 
since it could designate a new search space for finding lower bounds with a computer.

### 2021-04-14 article/weakschur.tex
reorganisation sat / search space

We first give an intuitive explanation of the above theorem. Let \((p, q) \in \mathbb{N}^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\) and let's try to build a colouring of \([\![1, ap + q]\!]\)
into \(n + k\) weakly sum-free subsets. Let \(l = a - b - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = b - r\). \\

@@

In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem. \\

\begin{remark}
This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\),
this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition
3.1)},we define \(\WS^+\) and find inequalities between \(\WS^+\),\(\WS\) and \(S\)
\end{remark}

@@

\textsc{Proof :}Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\
We denote by \(g\) the colouring associated to the partition of \([\![1,q]\!]\) and \(h\) the
one associated to the partition of \([\![1,p]\!]\).
\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a b-WSF-template.}
\]
\[h : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } h(x) = h(y)
\Longrightarrow h(x+y) \neq h(x)
\]

Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such that:
\\\\-if x \(\leqslant b \text{ (we will note x} \in \mathcal{T}): f(x)=g(x)\)
\\\\-if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
\\\\-if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{L}): f(x)=n-1+h(\lambda(x))\)
\\\\
f is well defined because \(\pi\) is defined for x\(>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because h(\(\lambda(x))\leqslant k\)

We have parted the integers of \(\![1,b+pa]\!]\) in three disjoints subsets \(\mathcal{T},\mathcal{C} \text{ and } \mathcal{L}\).

@@

\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{L}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\Then, f(x)=f(y)=n. We distinguish two cases:

@@

\underline{if (x,y) \(\in \mathcal{C} \times \mathcal{L} \), \(f(x)\neq f(y)\)}\\

\underline{if (x,y) \(\in (\mathcal{L})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\Let r(x)=\(\pi(x)-a\) and r(y)=\(\pi(y)-a\),
\\We proved that \(x=a\lambda(x)+\pi(x)-a\), therefore \(x=a\lambda(x)+\pi(x)\)
\\\(x+y=a(\lambda(x)+\lambda(y))+r(x)+r(y)\). We distinguish three cases:

@@

\item If \(r(x)+r(y)>b\), \(\pi(x)+\pi(y)>2a+b\)
\\Since g is a b-WSF template, \(g(\pi(\pi(x)+\pi(y))) \neq n\)
\\Therefore, \(g(\pi(x+y)) \neq n\) ie \(x+y \in \mathcal{C}\)
\\Hence \(f(x+y) <n\leqslant f(x)\)
\item If \(r(x)+r(y)\leqslant b-a,\), \(\pi(x)+\pi(y)\leqslant b+a\)
\\Since g is sum-free for x\(>b\), since \(g(\pi(x)) = g(\pi(y))=n\), \(g(\pi(x+y)) \neq g(\pi(x))=n\)
\\Hence, \(f(x+y) <n\leqslant f(x)\)
\end{itemize}

@@

The first two inequalities were found by Rowley, they are detailed in [2]. The third inequality is optimal and was found with a SAT solver.
It uses the first sophistication explained in the previous subsection in order to add the last number in the first color.
As for the fourth inequality, it was obtained by combining an optimal SF-template of length 33 with a WSF-template of length 4.
The best template we could get with a computer search gives the inequality \(\WS(n+4) \geqslant 127 S(n) + 68\).
It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of
5 colors which start with a good \(\WS(4)\) partition. However, this approach most likely prevents us from finding the best WSF-templates
as we explain in the next subsection for weakly sum-free partitions. We highly suspect that there exists more efficient WSF-templates
with \(n \geqslant 5\) colors. One may try to go over a different search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}.
This could be the suject of a future work. Further details about the encoding as a SAT problem can be found in the
\hyperref[SAT]{SAT section}. \\

Like in 3.3, we compute the lower bounds given by the previous inequalities for \( n \in [\![8,15]\!] \). The best lower bound
for each integer is highlighted.\\
\\
\begin{center}
\begin{tabular}{|*{5}{c|}}
    \hline
	n & 8 & 9 & 10 & 11 \\
	\hline
	\(4S(n-1) + 2 \) & 6722 & 21146 & \cellcolor{yellow} 71214 & \cellcolor{yellow} 243794\\
	\hline
	\(13S(n-2) + 8 \) & \cellcolor{yellow} 6976 & 21848 & 68726 & 231447\\
	\hline
	\(42S(n-3) + 24 \) & 6744 & \cellcolor{yellow} 22536 & 70584 & 222036 \\
	\hline
	\(127S(n-4) + 68 \) & 5656 & 20388 & 68140 & 213428\\
	\hline
	\hline
	n & 12 & 13 & 14 & 15 \\
	\hline
	\(4S(n-1) + 2 \) & \cellcolor{yellow} 815314 & 2554194 & 8045162 & \cellcolor{yellow} 27061154\\
	\hline
	\(13S(n-2) + 8 \) & 792332 & \cellcolor{yellow}2649772 & 8301132 & 26146778 \\
	\hline
	\(42S(n-3) + 24 \) & 747750 & 2559840 & \cellcolor{yellow} 8560800 &  25886224 \\
	\hline
	\(127S(n-4) + 68 \) & 671390 & 2261049 & 7740464 & 25886224 \\
	\hline
\end{tabular}
\end{center}

@@

>>>>

We give here an intuitive explanation of the above theorem; a formal proof can be found in the appendix. 
Let \((p, q) \in \mathbb{N}^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\) 
and let's try to build a colouring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let 
\(l = a - b - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = b - r\).

@@

In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem.

\begin{remark}
This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\),
this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition
3.1)}, we define \(\WS^+\) and find inequalities between \(\WS^+\),\(\WS\) and \(S\).
\end{remark}

@@

\textsc{Proof:} Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\
We denote by \(g\) the colouring associated to the partition of \([\![1,q]\!]\) and \(h\) the
one associated to the partition of \([\![1,p]\!]\).
\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a b-WSF-template.}
\]
\[h : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } h(x) = h(y)
\Longrightarrow h(x+y) \neq h(x)
\]

Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such that:
\\\\-if x \(\leqslant b \text{ (we will note x} \in \mathcal{T}): f(x)=g(x)\)
\\\\-if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
\\\\-if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
\\\\
f is well defined because \(\pi\) is defined for x\(>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because h(\(\lambda(x))\leqslant k\)

We have parted the integers of \(\![1,b+pa]\!]\) in three disjoints subsets \(\mathcal{T},\mathcal{C} \text{ and } \mathcal{R}\).

@@

\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{R}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\Then, f(x)=f(y)=n. We distinguish two cases:

@@

\underline{if (x,y) \(\in \mathcal{C} \times \mathcal{R} \), \(f(x)\neq f(y)\)}\\

\underline{if (x,y) \(\in (\mathcal{R})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\Let r(x)=\(\pi(x)-a\) and r(y)=\(\pi(y)-a\),
\\We proved that \(x=a\lambda(x)+\pi(x)-a\), therefore \(x=a\lambda(x)+\pi(x)\)
\\\(x+y=a(\lambda(x)+\lambda(y))+r(x)+r(y)\). We distinguish three cases:

@@

\item If \(r(x)+r(y)>b\), \(\pi(x)+\pi(y)>2a+b\)
\\Since g is a b-WSF template, \(g(\pi(\pi(x)+\pi(y))) \neq n\)
\\Therefore, \(g(\pi(x+y)) \neq n\) ie \(x+y \in \mathcal{C}\)
\\Hence \(f(x+y) <n\leqslant f(x)\)
\item If \(r(x)+r(y) \leqslant b - a\), \(\pi(x)+\pi(y)\leqslant b+a\)
\\Since g is sum-free for x\(>b\), since \(g(\pi(x)) = g(\pi(y))=n\), \(g(\pi(x+y)) \neq g(\pi(x))=n\)
\\Hence, \(f(x+y) <n\leqslant f(x)\)
\end{itemize}

@@

The first two inequalities were found by Rowley, they are detailed in [2]. The third inequality is optimal and was found with a SAT solver.
It uses the first sophistication explained in the previous subsection in order to add the last number in the first color.
As for the fourth inequality, it was obtained by combining an optimal SF-template of length 33 with a WSF-template of length 4.
The best template we could get with a computer search gives the inequality \(\WS(n+4) \geqslant 127 S(n) + 68\).
It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of
5 colors which start with a good \(\WS(4)\) partition. However, this approach most likely prevents us from finding the best WSF-templates
as we explain in the next subsection for weakly sum-free partitions. We highly suspect that there exists more efficient WSF-templates
with \(n \geqslant 5\) colors. One may try to go over a different search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}.
This could be the suject of a future work. Further details about the encoding as a SAT problem can be found in the
\hyperref[SAT]{SAT section}.

Like in 3.3, we compute the lower bounds given by the previous inequalities for \( n \in [\![8,15]\!] \). The best lower bound
for each integer is highlighted.

\begin{center}
\begin{tabular}{|*{5}{c|}}
    \hline
	n & 8 & 9 & 10 & 11 \\
	\hline
	\(4S(n-1) + 2 \) & 6722 & 21146 & \cellcolor{yellow} 71214 & \cellcolor{yellow} 243794\\
	\hline
	\(13S(n-2) + 8 \) & \cellcolor{yellow} 6976 & 21848 & 68726 & 231447\\
	\hline
	\(42S(n-3) + 24 \) & 6744 & \cellcolor{yellow} 22536 & 70584 & 222036 \\
	\hline
	\(127S(n-4) + 68 \) & 5656 & 20388 & 68140 & 213428\\
	\hline
	\hline
	n & 12 & 13 & 14 & 15 \\
	\hline
	\(4S(n-1) + 2 \) & \cellcolor{yellow} 815314 & 2554194 & 8045162 & \cellcolor{yellow} 27061154\\
	\hline
	\(13S(n-2) + 8 \) & 792332 & \cellcolor{yellow}2649772 & 8301132 & 26146778 \\
	\hline
	\(42S(n-3) + 24 \) & 747750 & 2559840 & \cellcolor{yellow} 8560800 &  25886224 \\
	\hline
	\(127S(n-4) + 68 \) & 671390 & 2261049 & 7740464 & 25886224 \\
	\hline
\end{tabular}
\end{center}

@@

\subsection{Conclusion on WSF-templates}

In this section, we first gave a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott 
and Hanson's construction for sum-free partitions. We then  introduced WSF-templates and generalized this construction. This 
allows us to find new lower bounds and new inequalities for weak Schur numbers. One may notice the significant difference 
between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds 
obtained with WSF-templates (including Rowley's two inequalities). In the next section, we try to analyze this phenomenon.
